Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-18 paper/main.tex
xi and bib:
rewrote cat intro

\usepackage[switch]{lineno}
\linenumbers

\begin{document}
%
\title{Topological Equivariant Artist Model for Visualization Library Architecture}
% author names and IEEE memberships
\author{Hannah~Aizenman, Thomas~Caswell, and~Michael~Grossberg,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem H. Aizenman and M. Grossberg are with the department of Computer Science, City College of New York. 
\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: haizenman@ccny.cuny.edu, mgrossberg@ccny.cuny.edu 
\IEEEcompsocthanksitem Thomas Caswell is with National Synchrotron Light Source II, Brookhaven National Lab 
\protect \\
E-mail: tcaswell@bnl.gov}% <-this % stops an unwanted space
\thanks{Manuscript received X XX, XXXX; revised X XX, XXXX.}
}

@@

\note{I've seen this convention before, but I also cite all these people above}
For more information on fiber bundles and sheaves, see Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, Spanier \cite{spanier1989algebraic} and Ghrist\cite{ghristElementaryAppliedTopology2014,ghristHomologicalAlgebraData2018}.

@@

For more information on category theory, see Barr and Wells\cite{barrCategoryTheoryComputing}, Fong and Spivak \cite{fongInvitationAppliedCategory2019}, Riehl\cite{riehlCategoryTheoryContext} and Bradley et. al. \cite{bradleyTopologyCategoricalApproach2020}.

\section{Artist} 
In this section, we use category theory to formally express the implicit assumptions that visualization library components make in transforming data into graphical representations. We propose that the visualization transformation can be modeled as a functor, which we call the \textcolor{artist}{Artist} \vartist \footnote{We call this transformation the artist because the \mintinline{python}{Artist} object in Matplotlib\cite{hunterMatplotlib2DGraphics2007}}. The artist \vartist\ converts data, which we model as the sheaf $\sheafc_{\dtotalc}$ to graphics in the sheaf $\sheafc_{\gtotalc}$. We formulate this association as

\begin{equation}
  \label{eq:artist:artist}
  \vartistc: \sheafc_{\dtotalc} \rightarrow \sheafc_{\gtotal}
\end{equation}

In this section we describe the structure of the data and graphic spaces, which we formulate as objects in categories and the morphisms between those objects. We then use these definitions to express the structure that an artist must preserve. Finally, we propose that artists can be composed by manufacturing new artists based on various types of input data.

>>>>

\usepackage[switch,columnwise]{lineno}

\begin{document}
\linenumbers

\title{Topological Equivariant Artist Model for Visualization Library Architecture}
% author names and IEEE memberships
\author{Hannah~Aizenman, Thomas~Caswell, and~Michael~Grossberg,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem H. Aizenman and M. Grossberg are with the department of Computer Science, City College of New York. 
\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: haizenman@ccny.cuny.edu, mgrossberg@ccny.cuny.edu 
\IEEEcompsocthanksitem Thomas Caswell is with National Synchrotron Light Source II, Brookhaven National Lab 
\protect \\
E-mail: tcaswell@bnl.gov}% <-this % stops an unwanted space
\thanks{Manuscript received X XX, XXXX; revised X XX, XXXX.}
}

@@

@@

\section{Artist} 
In this section we describe the properties a data to visualization transform must satisfy to be considered equivariant and continuity preserving. We propose that by explicitly defining these properties, we can better incorporate them into visualization library design.

We formulate the visualization transformation as a functor, which we call the \textcolor{artist}{Artist} \vartist \footnote{We call this transformation the artist because the \mintinline{python}{Artist} object in Matplotlib\cite{hunterMatplotlib2DGraphics2007}}. The artist \vartist\ converts\textcolor{total}{data}, which we denote $\mathcal{\dtotalc}$ to \textcolor{total}{graphics} $\mathcal{\gtotalc}$. We formulate this association as

\begin{equation}
  \label{eq:artist:artist}
  \vartistc: \mathcal{\dtotalc} \rightarrow \mathcal{\gtotalc}
\end{equation}

In this section we encapsulate the structure of the data and graphic spaces as categories. We then use these definitions to express the structure that an artist preserves. Finally, we introduce rules for composing artists in a way where the structure between the inputs to the individual artists is preserved.
